
%//////////////////////////////////////////////////////////////////////////////////////////
%////////////////////////////////////NOTABLE PROJECTS//////////////////////////////////////
%//////////////////////////////////////////////////////////////////////////////////////////

\section{NOTABLE PROJECTS}
\vspace{-4mm}

{\customcvproject{Low-Power Hardware/Software Co-design For Micro Plastics Filter}{2022}{42T}
  {\begin{itemize}
    \item Hardware Co-devloper and Lead Software Engineer on low-cost, highly embedded Electronics.
    \item Part of Product design team working entirely in-house, including mechanical and design engineers.
    \item No mains supply, required battery life of years. 
    \item Developed novel sensing algorithm for consumable depletion, specced circuit for implementation. 
    \item Designed PCB to support 9 different 8-Bit MCU varients with no software mods for supply chain resilience.
    \item Lead software development during mechanical prototyping and preparation for production. 
    \item Developed complete CI/CD framework supporting multiple hardware variants, unit testing, linting, docs. 
    \item Integrated late-stage support for writing debugging info to an SD Card for long-term testing.
    \item The product is now on sale, operating on our Hardware/Software, battery life of \~{3} years on 2 AAs. 
  \end{itemize} 
  }
}

{\customcvproject{Analogue Design for Low-Power Current Source for Fast Response Aerosol Heater}{2023 - 2024}{42T}
  {\begin{itemize}
    \item Worked under guidance of technical lead designing Temperature Controller and Power Supply for miniature Heating Element. 
    \item Performed Simulation work and Debugging of Current Source with 90\% Efficiency, 100\mu s response time. 
    \item Developed an analogue temperature controller using the voltage on the heater to perform PWM control. 
    \item Became system expert, lead day-to-day work, presented progress to client at bi-weekly project updates.
    \item Performed PCB Bring-up, modified the circuit to account for behaviours not observed in simulation. 
    \item Lead Validation, designed test plan, performed key validation, lead others on high-volume build testing. 
    \item Authored Technical Design Description and Manual provided to the client. 
  \end{itemize} 
  }
}

{\customcvproject{Administration of CI/CD System for Embedded Linux System}{2024}{42T}
  {\begin{itemize}
    \item Brought onto fast-moving product development project to improve Embedded Linux Software Process.
    \item Had to learn Jenkins and Yocto Project on the job. 
    \item Resurrected Jenkins CI/CD Setup left abandoned by past contractor. 
    \item Developed nightly-builds system using Jenkins/BitBucket.
    \item Produced custom Yocto Layers to add features \& make dependencies available to wider team. 
    \item Presented Yocto experience to wider software team. 
    \item Automated builds allowed all team members to re-flash the Linux SoM, greatly increasing project agility. 
  \end{itemize} 
  }
}

{\customcvproject{Software Development for Industrial Test Platform}{2023- 2024}{42T}
  {\begin{itemize}
    \item Project to develop a bespoke robotic platform tailored to our client's products. 
    \item Brought onto project part way through development as principal software engineer.
    \item Significant Modification to C\# WPF GUI and GALIL Robot Control Code. 
    \item In-depth testing on Calibration and Safety. 
    \item Lead live remote demo to client in U.S. broadcasting multiple camera angles of the system. 
    \item Client uses platform to produce empirical data on the quality of their product vs. competitors.
  \end{itemize} 
  }
}

{\customcvproject{Accelerating ML performance on an open-source RISC-V Core}{Sept 2020 - Feb 2021}{University - 4th Year Group Project}
  {\begin{itemize}
    \item Worked with a group of six as Hardware Benchmarking Lead.
    \item Added part of the RISC-V Vector Extension (RVV) to existing open-source RiSC-V core.
    \item Ported Tensorflow Lite for Microcontrollers (TFLM) and the TinyMLPerf benchmark to the processor.
    \item Liaised with the TFLM team at Google to integrate RVV instructions into TFLM. 
    \item Lead efforts to open source work at \url{github.com/AI-Vector-Accelerator}
    \item Presented work at British Computer Society Event. \url{youtu.be/t0Fpy4TzLUE}
    \item Final result: Measurable 7x speed up in TinyMLPerf performance over standard core.
  \end{itemize} 
  }
}

{\customcvproject{Light Opera Musical Director}{Oct 2019 - Feb 2021}
  {\begin{itemize}
    \item Led ~25 singers and 12 person orchestra to produce a successful operatic stage production.
    \item Managed performer disagreements, orchestra and cast recruitment, planning and running weekly rehearsals.  
    \item Liaised with show directors to manage rehearsal time and guide the direction of the overall project.
  \end{itemize}
  }
}


%//////////////////////////////////////////////////////////////////////////////////////////
%//////////////////////////////////END NOTABLE PROJECTS ///////////////////////////////////
%//////////////////////////////////////////////////////////////////////////////////////////
