
{\customcvproject{Light Opera Society Webmaster}{March 2018 - Present}{}
  {\begin{itemize}
    \item Responsible for the Society's website, social media, Wiki, and general tech support.
    \item Maintained and improved the nearly decade-old HTML/CSS/PHP/JavaScript website codebase.
    \item Worked with show producers to coordinate publicity efforts across platforms.
    \item Set up an AWS server to host a MediaWiki site.
    \item Provided online spaces for remote society activities during the COVID-19 pandemic. 
  \end{itemize}
  }
}

\section{ONGOING HOBBY PROJECTS}

{\customcvproject{3D Printer Bring-up}{}{}
  {\begin{itemize}
    \item I am currently building and optimising a budget 3D printer to support future hardware projects. 
    \item Will be used to support upcoming personal projects and home maintenance tasks.
    \item Modifications include adding Raspberry Pi for remote monitoring and control.
    \item Parts will be designed for printing in Fusion360 and FreeCAD.
  \end{itemize}
  }
}

{\customcvproject{Electronic Hurdy Gurdy (Musical Instrument) Development}{}{}
  {\begin{itemize}
    \item The Hurdy Gurdy is a medieval stringed instruments which can play melody and rhythmic drones.
    \item The melody is played with a button board, the drone by varying the turning speed of a hand crank.  
    \item They are very expensive so I want to develop a cheap, electronic version for personal use.
    \item This project will test my skills in real-time firmware, mixed-signal electronics, and 3D design. 
    \item This project is the main use for the 3D printer discussed above.
    \item I will start with an open-source design for a simple MIDI controller.
    \item I will then add firmware and hardware features to suit my needs and style of play as they occur to me. 
    \item This would include a TFT screen interface, an in-built MIDI synthesiser, and CAN bus/Bluetooth connectivity to external input devices.
    \item It will provide the experience iterating on the design over a long period that the short-term projects completed at University could not provide.
  \end{itemize}
  }
}

{\customcvproject{Learning the Rust Programming Language}{}{}
  {\begin{itemize}
    \item Rust's unique safety features make it a compelling hosted and embedded systems development.
    \item I have been working through ``The Rust Book'', the official step-by-step tutorial.
    \item I think Rust has a serious future in systems development, but learning about it's benefits over C/C++ has also helped me understand the shortcomings of those languages.
    \item I aim to use Rust both in stand-alone projects and to create high-speed Python bindings. 
  \end{itemize}
  }
}

{\customcvproject{Learning Embedded Linux}{}{}
  {\begin{itemize}
    \item Due to lecturer strikes in my 2nd and 3rd year, Embedded Linux was not covered in detail at Southampton.
    \item To compensate for this, I am following online tutorials and resources to learn this missing skill.
    \item I have been using Buildroot to build Linux images from source for Raspberry Pi devices.
    \item This skill will be useful both in my career and in hobby projects.
    \item It provides a relatively easy way to integrate hosted-style networking and multi-tasking capabilities into relatively low-power projects. 
  \end{itemize}
  }
}

