%//////////////////////////////////////////////////////////////////////////////////////////
%////////////////////////////////////////SKILLS////////////////////////////////////////////
%//////////////////////////////////////////////////////////////////////////////////////////

\section{SKILLS}
\begin{minipage}{\maincolumnwidth}%
	\small{
    	\begin{itemize}
        \item \textbf{Notable Areas of Experience:} Embedded and Hosted Software Development, Mixed Signal Electronics, PCB Design, Bring-up \& Debugging, DevOps CI/CD, Embedded Linux, Rapid Prototyping.
        \item \textbf{Language Proficiencies:} C/C++, Python, MATLAB/Octave, Bash Scripting, Web Dev, C\#, Rust.
        \item \textbf{Software:} KiCad EDA, LTSpice Circuit Sim, GIT, BitBucket, Jenkins
        \item \textbf{Environments/Frameworks:} Linux/Unix, Docker, Yocto Embedded Linux, Qt/PyQt, MicroPython.
		\end{itemize}}%
\end{minipage}
      

%//////////////////////////////////////////////////////////////////////////////////////////
%/////////////////////////////////////END SKILLS///////////////////////////////////////////
%//////////////////////////////////////////////////////////////////////////////////////////

%//////////////////////////////////////////////////////////////////////////////////////////
%///////////////////////////////////////EXPERIENCE/////////////////////////////////////////
%//////////////////////////////////////////////////////////////////////////////////////////

\section{EXPERIENCE}
{\customcventry{Oct 2021 - Present}{Consultant - Electronics}{\href{https://42t.com/}{42T}}{St Ives - Cambridgeshire}{}
  {\begin{itemize}
      \item Working with cross-disciplinary teams solving complex problems for clients in a variety of industries. 
      \item Electronics Hardware Development - Simulation, Schematic Capture \& Layout, PCB Manufacture \& Debugging.
      \item Software Development - Bare-metal MCU, Hosted Linix/Windows, Prototype through to Production Quality. 
      \item DevOps and Software Quality - Company Expert on CI/CD Pipelines, C \& Python Unit Testing, Docker.
      \item Embedded Linux CI/CD - Administered Jenkins System for Nightly \& on-demand builds, added Yocto Layers.
      \item Regular presentations to clients communicating technical info to non-subject specialists.
      \item Co-running Graduate Technical Interviews, Mentoring Graduate Hires, Attending Job Fairs. 
  \end{itemize}
  }
}
  
{\customcventry{June 2020 – Sept 2020}{Systems Engineering Intern}{\href{https://iter-systems.com}{ITER Systems SARL}}{Remote}{}
  {\begin{itemize}
      \item Completed smaller hardware/software projects so full-time employees could focus on long-term projects.
      \item Developed cross-compilation workflow (Windows 10 to embedded Linux) for an existing Qt-based software suite.
      \item Tested GSM hardware for use with Raspberry Pi (and similar) systems.   
      \item Developed next-generation software for autonomous boat position tracking and bathymetric data presentation.
      \item Full reference available on request.
  \end{itemize}
  }
}

%//////////////////////////////////////////////////////////////////////////////////////////
%////////////////////////////////////END EXPERIENCE////////////////////////////////////////
%//////////////////////////////////////////////////////////////////////////////////////////

%//////////////////////////////////////////////////////////////////////////////////////////
%//////////////////////////////////////EDUCATION///////////////////////////////////////////
%//////////////////////////////////////////////////////////////////////////////////////////

\section{EDUCATION}
{\customcventry{July 2021}{MEng Electronics with Computer Systems: 1st Class Honors}{University of Southampton}{Southampton, UK}{}{}}

%//////////////////////////////////////////////////////////////////////////////////////////
%////////////////////////////////////END EDUCATION/////////////////////////////////////////
%//////////////////////////////////////////////////////////////////////////////////////////

